Data Structures Comparative Review Thing

### 2014-04-15 paper/paper.tex
Wrote some more on the paper.

    We used C++ as the implementation language.  libstdc++'s implementations of the standard
    class templates \texttt{std::map} and \texttt{std::unordered\_map} were used for the binary search
    tree and the hash table respectively.  As the C++ standard library lacks a skip list\footnote{reference to
    the standard here}, we used an open-source third party library, \texttt{CSSkipList}\footnote{reference to
    library home page here}.

@@

@@

>>>>

    We used C++ as the implementation language.  libstdc++'s implementations of the standard class
    templates \texttt{std::map} and \texttt{std::unordered\_map} were used for the binary search
    tree and the hash table respectively.  As the C++ standard library lacks a skip
    list\footnote{reference to the standard here}, we used an open-source third party library,
    \texttt{CSSkipList}\footnote{reference to library home page here}.  We also used libstdc++'s
    implementation of \texttt{std::string} for our string handling needs.

@@

    For our data, we took the system's dict file and the list of top level domains from Wikipedia
    and combined the two to generate a bunch of things of the form \texttt{www.\$word.\$tld}, where
    \texttt{\$word} is one of the dictionary words and \texttt{\$tld} is a top level domain.  Only
    words consisting of the lowercase letters \texttt{a} through \texttt{z} were used.  Words were
    limited to be from 8 to 12 characters and top-level domains were limited to exactly two letters.
    All possible combinations were generated.  For the full paths, a number of domains were selected
    and each was appended some number of random alphanumeric strings of eighty characters.  For more
    details, see the code.

    After some test runs we chose to decrease the number of runs used for measurements.  In the
    proposal we had said that for each time measurement we would perform the relevant operation 1000
    times and then take the average of that.  In practice, this made the tests run for longer than
    we could afford and the results given by running 100 times were comparable so we only ran that
    many times.  We expect the general result to be the same; see some later section for details
    about what \emph{could} have gone wrong.

@@

    Also, we have counterintuitive results that show that inserting or querying a full path is
    faster than querying only the domain name.  This can partially be explained\footnote{Not really,
    but ehhh.} by the fact that the string implementation we used was based on reference counting.
    (If it'd also provide SSO, this would be easy to explain, but the darn thing doesn't.)
